% !TEX root = ../report.tex

\chapter{Evaluation}
\label{chap:resulteval}
\minitoc

%TODO intro

\clearpage

\input{masterChapters/05-result-evaluation/experimental-results}




\section{Discussion}

In Chapter 1 we introduced a total of 8 goals for our Master's thesis:

\begin{itemize}
\item G1: Gain a better understanding of the fashion domain.
\item G2: Identify the specific challenges of making fashion recommendations.
\item G3: Study how existing technologies can be adapted to mitigate or
  		  overcome these challenges.
\item G4: Study existing solutions to the cold-start.
\item G5: Identify the best suited methods with regard to both application and domain.
\item G6: Explore the existing solutions of how to infer user preference from implicit feedback data.
\item G7: Establish user interaction patterns to support our assumptions.
\item G8: Find different methods of combining various event types into implicit ratings.
\item G9: Find metrics in order to evaluate the \emph{implicit ratings}
\end{itemize}

In the following subsection we will reiterate these goals and discuss whether we have succeeded in reaching our goals. Readers should
note that we already have performed a detailed analysis of the results of the work on goals G1 in Section \ref{subsec:fashion-theory} and \ref{chap:thesobazaardata},
G2 in Section \ref{subsec:fashion-theory} and \ref{chap:thesobazaardata}, G3 in Section \ref{subsec:fashion-theory}, G4 and G5 in Section \ref{sec:cold-start-discussion}, G6 in Section \ref{implicit-weaknesses},
G7 in Section \ref{}, G8 in Section \ref{} and finally G9 in Section \ref{sec:evaluation-metrics}.
The following discussion will therefore be fairly high-level, and avoid the \emph{nitty-gritty} details.

\subsection{G1, G2 and G3: Solutions to the fashion domain related problems}
\label{sec:fashion-discussion}

Through thorough examination and analysis of the data and a literature review of fashion articles we came to the following main conclusions:
incorporating more data to a sparse data set is essential,
time is central, both when it comes to the users and the items,
and fashion is built on subcultures.

After analyzing the data it became apparent that the data was not just sparse in the sense of users, but also in the sense of items and item interactions.
Working with purchases alone would render the data too sparse to be able to retrieve any good results, so more data was needed.
Clicks and want naturally had a higher interaction rate, and proved to be usable data in the sense of user preferences, and this should be used to supplement the low purchase data.

Another interesting find when looking at the data was the importance of time, and its relevance to the fashion domain.
Many of both the user accounts and the items are short lived, and the decaying factor must generally be handled when doing recommendations in the fashion domain.
The recommendation system should therefore be supplemented with the concept of time, and handle the average items' natural loss of attention over time.

Looking at the fashion domain we saw how significant the idea of subcultures are for the fashion domain, and that purchasing fashion articles are not just done for the need, but for the \emph{belongingness} and to show off.
Based on these findings we expect recommendations to greatly benefit from capturing these subcultures and utilizing them to improve user preference understanding, and thereby improve recommendations done to the users.

%Important notes

\subsection{G4: The Cold-Start Problem}
\label{sec:cold-start-discussion}

Through our literature review, we closely examined five different classes of solutions to the cold-start problem. Namely trust-aware recommender system, filterbots, seed users, interview process and hybrid methods.

However, a question that should be asked is whether there exists and solutions which we did not discover or was excluded from our review. An issue that could have influenced the results of our review is \emph{researchers bias}, which could have arisen of any of the researchers had preferences for one of the solution types before the literature search. The reason for including multiple methods that never were used was due to uncertainty regarding what data would become available during the project. Trust-aware recommender system and hybrid methods in particular could never be tested out due to a lack of social/demographic data, which we were hoping to get access to.



After closely examining the different methods we concluded that both filterbots and content-boosted hybrid methods could provide a possible solution for
our specific scenario...

Demographic information could further improve its performance and usefulness. Agarwal et. al. \cite{Agarwal2009} used 13 filterbots in their experiments, where 11 out of 13 bots rated items based on demographic information.


\subsection{G5, G6, G7: Implicit Ratings}
\label{sec:implicit-discussion}

Importance of implicit factors for the domain

Another question that arises is: when does it become obsolete to look at clicks and wants?

%TODO - Discuss implicit ratings





\section{Issues}\label{sec:issues}

%TODO - Mention that the recommender system libraries are terribad for evaluation...
