\section{Experimental Plan}

%Our experiment aims to uncover...


\section{Selecting datasets for evaluation}

In addition to evaluate the methods on the Sobazar dataset we want to make sure that our solution generalizes beyond our experimental dataset, in accordance to the general guidelines for experimental studies \ref{Shani2011}.

The data used for offline evaluation should match as closely as possible the data we expect the recommender system to face when it is deployed \cite{Gunawardana2009}. However, most publicly available datasets are not collected from e-commerce sites and does therefore not contain user browsing history, purchases etc. 


Natural to assume that the number of users on Sobazar will increase as they system \emph{officially} goes live.

%Always a possibility to reduce the size of datasets by removing some ratings...




When selecting datasets for evaluation we focused on the following dataset properties:

\begin{itemize}
	\item Size of dataset: Preferable as close as possible to Sobazar in terms of number of ratings, users and items.
	\item Type of user feedback: Preferably implicit, as it allows us to test our implicit feedback to implicit rating function.
	\item Domain: E-commerce datasets with purchase history would be most relevant.
	\item Precence of features: To evaluate hybrid methods?
\end{itemize} 





\subsection{Dataset 1}

Rossmann dataset?
%General statistics and averages
%Interesting findings/properties
%Was cleaning neccesary?
%How was the methods evaluated on the dataset?
%	- x-fold cross validation

\subsection{Dataset 2}

Movielens/Million Song dataset?
%General statistics and averages
%Interesting findings/properties
%Was cleaning neccesary?
%How was the methods evaluated on the dataset?
%	- x-fold cross validation

\subsection{Sobazar Data}

%Highlight limitations of the sobazar dataset for evaluation

%-> Implications for evaluation
%How was the methods evaluated on the dataset?
%	- x-fold cross validation

\subsection{Summary}

%Some fancy tables n stuff

%TODO - What else is interesting to know? Rating scale, average number of ratings per user, number of cold start users...

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
	Dataset		& 	Ratings & 	Users	& 	Items 	& 	Sparsity 	\\ \hline
	Sobazar 	& 	15,252  & 	1,235	&	3,386	&	-			\\ \hline
	Dataset 1 	& 	-  		& 	-		&	-		&	-			\\ \hline
	Dataset 2 	& 	-  		& 	-		&	-		&	-			\\ \hline
    \end{tabular}
    \label{table:datasets}
    \caption [Overview of the datasets used for evaluation]{Overview of the datasets used for evaluation}
\end{table}


\section{Simulating the cold-start problem}

%Describe the methodology used to simulate the cold-start problem
%	- Why did we choose this methodology?
%	- How to split the dataset
%	- 


\subsection{Evaluation Metrics}