\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,oneside]{report}

\usepackage[section] {placeins}
\usepackage{amsmath} % math symbols
\usepackage{booktabs} % commands to better structure tables
\usepackage[english]{babel} % break words when going over a line.
\usepackage{caption}
% \usepackage{cite} % we want to cite our bibliography
\usepackage{enumerate} % we want lists.
\usepackage{enumitem} % less gap between items
\usepackage{fancyhdr}
\usepackage{fancyvrb} % for fancy verbatims and centering them
\usepackage{float} % for placing figures/tables at the specified place in text with [H]
%\usepackage[headings]{fullpage} % wider
\usepackage[top=2in, bottom=1.5in, left=1in, right=2in]{geometry}
\usepackage{graphicx} % in order to insert images
\usepackage[linkcolor={blue},citecolor={blue},urlcolor={red}]{hyperref}
\usepackage{listings} % to add code snipes and such
\usepackage{minitoc}
\usepackage{natbib} % citep used when author-date citation styles are required?
\usepackage{pgfplots} % in order to create nice tikz plots
\usepackage{pgfplotstable}
\usepackage{pgf-pie}
\usepackage{tablefootnote} % for handling footnote in tables
\usepackage{tabularx}
%\usepackage{todonotes} % todo boxes
\usepackage{soul}
\usepackage{subcaption}
\usepackage{verbatim} % Enable verbatim text for code etc.
\usepackage{pbox}     % Can be used in tables to have multiple lines in one box
\usepackage{multirow} % Span a row over multiple rows
\usepackage{amssymb}
\usepackage{pifont}   % Can add check symbol
\usepackage{tikz}
\usetikzlibrary{calc,trees,positioning,arrows,chains,shapes.geometric,%
    decorations.pathreplacing,decorations.pathmorphing,shapes,%
    matrix,shapes.symbols}
% \usepackage[utf8]{inputenc}
%\usepackage[dvipsnames]{xcolor}
\pgfplotsset{compat=1.9} % latex suggest for compatibility

\pagestyle{headings} % Footer is blank, header displays information according
% to document class (e.g., section name) and page number top right.
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\dualGraphWidth}{3.1in} % to make dualgraph look similar
\newcommand{\graphWidth}{5in} % to make dualgraph look similar
\newcommand{\cmark}{\color{ForestGreen}\ding{52}} % Awesome green check mark
\newcommand{\xmark}{\color{RedOrange}\ding{55}}   % Awesome red cross mark
% Package configutations
\newcommand{\notimplies}{\mathrel{{\ooalign{\hidewidth$\not\phantom{=}$\hidewidth\cr$\implies$}}}}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Header
\lstset{
  basicstyle=\ttfamily\tiny,
  breaklines=true,
  aboveskip=25pt,
  belowskip=25pt
} % code box
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue
\restylefloat{table}

%Quotes
\makeatletter
\renewcommand{\@chapapp}{}% Not necessary...
\newenvironment{chapquote}[2][2em]
  {\setlength{\@tempdima}{#1}%
   \def\chapquote@author{#2}%
   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
   \itshape}
  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

% Custom variables
\def \thesistitle{Fashion recommendations using small implicit datasets}
\def \authorname{Thomas Almenningen, Martin Christian Havig and Herman Schistad}
\def \supheri{Heri Ramampiaro}
\def \suphelge{Helge Langseth}
\def \degreename{Computer Science}
\def \groupname{Artificial Intelligence Group}
\def \deptname{IDI}

% \newcommand*{masterChapters}{chapters}

% PDF-metadata
\hypersetup{pdftitle={\thesistitle}}
\hypersetup{pdfauthor=\authorname}

\begin{document}

%----------------------------------------------
% TITLE PAGE
%----------------------------------------------

\begin{titlepage}
\begin{center}
\mbox{}\\[6pc]
\begin{center}
\Huge{\thesistitle}\\[2pc]

\Large{\authorname}\\[1pc]
\large{\today}\\[2pc]

MASTER THESIS\\
Department of Computer and Information Science\\
Norwegian University of Science and Technology
\end{center}
\vfill

\noindent Principal supervisor: \suphelge \\
\noindent Secondary supervisor: \supheri

  %{\Huge Twilm} \\
  %\medskip
  %  \vspace{\stretch{0.2}}
%
 %   { \Large \bfseries PROJECT}
  %  \HRule \\[0.5cm]
  %{ \huge \bfseries ONELINER ABOUT \\[0.4cm]}

   % \HRule \\[0.5cm]

   % \begin{minipage}{0.4\textwidth}
   %     \begin{flushleft} \large
   %         \emph{Authors}\\
   %         Martin Christian \textsc{Havig} \\
   %     \end{flushleft}
   % \end{minipage}
   % \begin{minipage}{0.4\textwidth}
   %     \begin{flushright} \large
   %         \emph{Supervisor:} \\
   %         Some  \textsc{One}
   %     \end{flushright}
   % \end{minipage}

    %\vfill
   % \today \\\ \\\
\end{center}
\end{titlepage}

\clearpage

%----------------------------------------------
% ACKNOWLEDGEMENTS
%----------------------------------------------

\renewcommand{\abstractname}{Acknowledgments}
\begin{abstract}

Our deepest gratitude goes to our supervisors at NTNU \textit{Heri Ramampiaro}
and \textit{Helge Langseth}, who throughout nearly a full year of research has
not only supported us, but with their enthusiasm and knowledge made us
understand and appreciate the field of recommender systems.

Equally our sincerest appreciation to our supervisor at Telenor Research
\textit{Hai Thanh Nguyen}, who has given us valuable insight and guidance
through weekly meetings the last six months. Not only has his expertise in the
field of machine learning made our end result better, but his role as
coordinator between; the Sobazar headquarters in Oslo; various researchers at
Telenor; and our supervisors at NTNU have been invaluable.

In addition, we thank \textit{Anders Kofod-Petersen} who has given his
constructive and useful insights on a range of topics spanning from the layout
and focus of our thesis to inner workings of algorithms and metrics. We also
thank \textit{Humberto Castejon} and \textit{Cyril Banino-Rokkones} for their
support and ideas when initiating this project. Valuable input and help was
provided by the Sobazar team and especially \textit{Markus Krüger} and
\textit{Matias Holte} who we had a meaningful and interesting meeting with
halfway through. Finally our thanks to \textit{Rana Juwel} who has assisted us
with regards to content-based approaches for recommending based on the
Sobazar-dataset.

There are many to thank, but in summary we had the luxury of having multiple
researchers and supervisors, not only interested in the project, but in helping
us throughout these last months. We are grateful for all your support and
contributions. Again, thank you.

\end{abstract}

%----------------------------------------------
% ABSTRACT
%----------------------------------------------

\renewcommand{\abstractname}{Abstract}
\begin{abstract}

In recommender systems we seek to predict the rating or preference that a user
would give to an item. With the advent of modern application such as movie and
music streaming, E-commerce, social networks and many other platforms –
recommender systems have gained an important role in both a commercial and
academic setting. When analyzing various approaches to \textit{how} an
application generates recommendations, the prevalent technique is explicitly
asking the users for a numeric rating for every item they consume and from
these observed explicit ratings predict how the user would rate other items.
However, this procedure often requires important changes to the application
frontend and also an active effort from all users. In this thesis we instead
look at how these ratings can be inferred from looking at session data and the
transaction history for every user.

We analyze which recommender models are suitable for such an untraditional data
source, whilst accounting for a sparse dataset with few events – often called a
cold start environment. Multiple novel ways of generating ratings are presented
taking into account recentness in the data as an important factor. This,
combined with traditional recommender system approaches makes for a new and
interesting way of making recommendations in small datasets with high sparsity.
We then provide valuable insight into using and evaluating implicit ratings in
recommender system algorithms, spanning from simple global-averages to
state-of-the-art matrix-factorizations. A promising result is finally made,
supported by a range of relevant metrics, promoting further research into the
area of implicit ratings on sparse and small datasets.

Finally, a discussion is made on the various evaluation metrics for both
implicit ratings and our recommender models, as here as well the untraditional
approach of choosing implicit ratings as input to our models makes many of the
conventional metrics inefficacious.

\marginpar{heri-notes: Hovekonklusjon og hovedfunnene skal med her}

\end{abstract}
\pagenumbering{roman}

%----------------------------------------------
% TABLE OF CONTENTS
%----------------------------------------------

\setcounter{tocdepth}{2}
\dominitoc
\minilof
\minilot
\tableofcontents
\clearpage
\listoffigures
\listoftables

\setcounter{tocdepth}{1}

%----------------------------------------------
% CHAPTERS
%----------------------------------------------

\input{masterChapters/01-introduction}
\input{masterChapters/02-soBazarData}
\input{masterChapters/03-stateOfTheArt}
\input{masterChapters/04-algorithmic-background}
\input{masterChapters/06-implementation}
\input{masterChapters/07-result-evaluation}
\input{masterChapters/08-conclusion}
\input{masterChapters/99-appendices}

%----------------------------------------------
% BIBLIOGRAPHY
%----------------------------------------------
\clearpage
\addcontentsline{toc}{chapter}{References}
\bibliographystyle{plain}
\bibliography{references}

\end{document}
